Spin canonical divisors of log stacky curves

### 2015-06-20 stacky_write_up/spin_cring.tex
not editing section 3
O'Dorney's base case in section 3

%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%%%
%%%%%%%%%%%%%

@@

Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
 must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
is linearly equivalent to an effective $X$ divisor plus $\sum 
\subhalf{i}P_i$.  We have now reduced to the case of $\halfcan$ 
linearly equivalent to an effective divisor.  The result in this 
specific case in fact generalizes to any $\mathbf{Q}$-divisor: $\sum
\frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.

To prove thisUsing induction, we can prove prove that $\halfcan$ is 
generated up to degrees $e$ with relations up to degree $2e$.  
O'Dorney \todo{Insert reference} proves

>>>>

%%%%%%%%%%%%%%%%%%%%%%% amsthm theorem styles %%%%%%%%
%%%%%%%%%%%%%%%

@@

Since all $e_i$s are odd, $2$ cannot appear in a denominator of the 
coefficient of a point $P$ in $\halfcan$, meaning that $\frac{D}{2}$
 must be a $X$-divisor.  Since $\deg(\frac{D}{2})=\frac{1}{2}\deg(D)
\ge -\frac{1}{2}$, we in fact have $\deg(D)\ge 0$.  Thus $\halfcan$ 
is linearly equivalent to an effective $X$ divisor plus $\sum 
\subhalf{i}P_i$.  We have now reduced to the case of $\halfcan$ 
linearly equivalent to an effective divisor.  The result in this 
specific case in fact generalizes to any $\mathbf{Q}$-divisor: $D=\sum
\frac{\alpha_i}{\beta_i} P_i$ for $\alpha_i,\beta_i\in \mathbf{N}$.

We will sketch a proof by induction.  O'Dorney \todo{Insert reference to Theorem 4} provides a base case when $D\sim \frac{\alpha}{\beta} P$.  He finds generators in degrees up to $\beta$ and relations that are all quadratic in the generators (and thus lying in degrees at most $2\beta$).  We can ind
